Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-08 thesis/chapters/ch_chapter1.tex
First pass at adding in a chapter. Some of the refs are broken.

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\pdfoutput=1 
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{newtxtext,newtxmath}

%\usepackage{amsmath,amstext}
%\usepackage[T1]{fontenc}
\usepackage[figure,figure*]{hypcap}

%\hypersetup{draft}
%\usepackage{multirow}
%\usepackage{mathtools}
%\renewcommand*{\sectionautorefname}{Section} %for \autoref
%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
%\usepackage{graphicx}
%\usepackage{natbib} % bibliography

%\usepackage[active,floats,tightpage]{preview}
%    \setlength\PreviewBorder{1em}

\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}

\author[A. Emerick et. al.]{
Andrew Emerick,$^{1,2}$
Greg L. Bryan,$^{1,3}$
and Mordecai-Mark Mac Low$^{2,1,3}$
\\
$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}

\begin{document}

\label{firstpage}
%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

%\author{Andrew Emerick}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\author{Greg L. Bryan}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
%\author{Mordecai-Mark Mac Low}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}

\begin{abstract}
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

\begin{keywords}
Galaxy -- Hydrodynamics -- Simulation -- Feedback
\end{keywords}

\section{Introduction}
%
% AE removed below.. MM suggested  skipping both pars.
%
%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade. Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc. \citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses. On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM. This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}. See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics. 
%
%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution. In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense. In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships. For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.

Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single white dot.}
\label{fig:panel_x}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
\label{fig:panel_z}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
\label{fig:scale_height}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snrx100}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins. Broken portions of this histogram are time periods with no star formation or supernovae.  Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR. Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr. The dashed lines are lines of constant pressure, separated by factors of 10. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
\label{fig:phase}
\end{figure}

@@

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
\label{fig:ISM_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity. In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
\label{fig:ISRF}
\end{figure}

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.45\linewidth]{total_mass_outflow}
\includegraphics[width=0.45\linewidth]{total_mass_loading}
\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:mass_outflow}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. This is averaged over the same time interval as Fig.~\ref{fig:ISRF}. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM.}
\label{fig:outflow_velocity}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_retention}
\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.98\linewidth]{log_NO_panel}
\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances. The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right. In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
\label{fig:metal_slices}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. See text for details of the calculation. Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars. On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}. There is no clear correlation with time in this diagram.}
\label{fig:KS}
\end{figure*}

@@

%\bibliographystyle{yahapj}
\bibliographystyle{mnras}
\bibliography{msbib}

@@

\begin{figure*}
\centering
\includegraphics[width=0.4\linewidth]{Q0}
\includegraphics[width=0.4\linewidth]{Q1}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{L_FUV}
\includegraphics[width=0.4\linewidth]{L_LW}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{E0}
\includegraphics[width=0.4\linewidth]{E1}
\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right). Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
\label{fig:stellar radiation properties}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.4\linewidth]{sn_density_hist}
\includegraphics[width=0.4\linewidth]{sn_radius_hist}
\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation. {\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region. The vertical lines show one and 4.5 cell widths. This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
\label{fig:SN histogram}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background. Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e. optically thin) metal line cooling rates. The regimes where heating dominates are plotted with dashed lines for clarity.}
\label{fig:cooling comparison}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{cooling_curve}
\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}. The absolute value of the net cooling or heating
rate is shown with solid lines.}
\label{fig:cooling}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction. We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
\label{fig:Grackle grid}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted). The line colors in the left panel are for better clarity between the SFRs.}
\label{fig:resolution_study}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{3pc_phase.png}
\includegraphics[width=0.475\linewidth]{6pc_phase.png}
\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
\label{fig:phase_resolution}
\end{figure*}

@@

\label{lastpage}

\end{document}

>>>>

\chapter[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars \label{ch:chapter1}}
\let\thefootnote\relax\footnotetext{This section contains text from an article published in \cite{Emerick2019}}

%
% Copy paste paper here, without abstract or keywords
%
%
% Abstract left here for documenation purposes
%
%\begin{abstract}
%In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
%\end{abstract}

\newcommand{\ccunit}{cm$^{-3}$}

\section{Introduction}
Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{figures/ch1/multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single white dot.}
\label{fig:panel_x}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{figures/ch1/multiplot_4x4_z.png}
\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
\label{fig:panel_z}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{figures/ch1/scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
\label{fig:scale_height}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/sfr_snrx100}
\includegraphics[width=0.475\linewidth]{figures/ch1/mass_evolution}
\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins. Broken portions of this histogram are time periods with no star formation or supernovae.  Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR. Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{figures/ch1/phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr. The dashed lines are lines of constant pressure, separated by factors of 10. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
\label{fig:phase}
\end{figure}

@@

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{figures/ch1/phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{figures/ch1/phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
\label{fig:ISM_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{figures/ch1/G_o_profile} \\
\includegraphics[width=0.95\linewidth]{figures/ch1/ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity. In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
\label{fig:ISRF}
\end{figure}

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{figures/ch1/g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{figures/ch1/q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_outflow}
\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_loading}
\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:mass_outflow}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{figures/ch1/velocity_distribution_time_average}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. This is averaged over the same time interval as Fig.~\ref{fig:ISRF}. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM.}
\label{fig:outflow_velocity}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{figures/ch1/metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{figures/ch1/metal_retention}
\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.98\linewidth]{figures/ch1/log_NO_panel}
\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances. The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right. In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
\label{fig:metal_slices}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_schmidt_law_evolution.png}
\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_efficiency_evolution.png}
\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. See text for details of the calculation. Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars. On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}. There is no clear correlation with time in this diagram.}
\label{fig:KS}
\end{figure*}

@@

%\bibliographystyle{yahapj}
%\bibliographystyle{mnras}
%\bibliography{msbib}

%************* APPENDICES ************************%

%\clearpage
%\appendix

@@

\begin{figure*}
\centering
\includegraphics[width=0.4\linewidth]{figures/ch1/Q0}
\includegraphics[width=0.4\linewidth]{figures/ch1/Q1}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{figures/ch1/L_FUV}
\includegraphics[width=0.4\linewidth]{figures/ch1/L_LW}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{figures/ch1/E0}
\includegraphics[width=0.4\linewidth]{figures/ch1/E1}
\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right). Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
\label{fig:stellar radiation properties}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.4\linewidth]{figures/ch1/sn_density_hist}
\includegraphics[width=0.4\linewidth]{figures/ch1/sn_radius_hist}
\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation. {\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region. The vertical lines show one and 4.5 cell widths. This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
\label{fig:SN histogram}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch1/cooling_model_comparison}
\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background. Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e. optically thin) metal line cooling rates. The regimes where heating dominates are plotted with dashed lines for clarity.}
\label{fig:cooling comparison}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch1/cooling_curve}
\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}. The absolute value of the net cooling or heating
rate is shown with solid lines.}
\label{fig:cooling}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{figures/ch1/fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction. We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
\label{fig:Grackle grid}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.33\linewidth]{figures/ch1/sfr_resolution_study.png}
\includegraphics[width=0.33\linewidth]{figures/ch1/mass_evolution_resolution.png}
\includegraphics[width=0.33\linewidth]{figures/ch1/metal_retention_resolution.png}
\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted). The line colors in the left panel are for better clarity between the SFRs.}
\label{fig:resolution_study}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{figures/ch1/3pc_phase.png}
\includegraphics[width=0.475\linewidth]{figures/ch1/6pc_phase.png}
\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
\label{fig:phase_resolution}
\end{figure*}

@@

%\label{lastpage}

\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}

\renewcommand\thesection{\thechapter.\arabic{section}}
